\center \fontsize{18}{20} \selectfont Revealing the Landscape of Globally Color-Dual Multi-loop Integrands

### 2023-09-28 notes/2loopNLSM.tex
fresh pull
added CS appendix

Here we can think of the abelian vector as a background field that
sources on-shell $A_\mu$ currents. Indeed, as we describe in
\cref{sec:CKLagrangians}, semi-abelian Yang-Mills theory is at the
heart of $YZ$-theory \cite{Cheung:2016prv}, $J$-theory
\cite{Cheung:2020djz,Cheung:2021zvb}, and self-dual Yang-Mills
\cite{Monteiro2011pc}.  Specifically, semi-abelian YM is simply a
clever reinterpretation of the Lagrangian obtained by integrating an
auxiliary field into the $J$-theory equations of motion.  The Feynman
rule for the cubic vertex is
\begin{equation}
  \cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{}= (\varepsilon_1\bar{\varepsilon}_3)(\varepsilon_2 k_3)
  -  (\varepsilon_2\bar{\varepsilon}_3)(\varepsilon_1 k_3)
\end{equation}
where the incoming arrow is the abelianized gauge field, and the outgoing arrows the on-shell non-abelian vectors. The propagator is simply
\be
\propFrule{$A^\nu$}{$\bar{A}^\mu$}{$k \rightarrow $}{fermion2} = \frac{i}{k^2} \eta^{\mu\nu}.
\ee
We can use the Ward identity of
\cref{eq:GIrelA} to check that the amplitudes are indeed gauge
invariant when the \emph{abelian} polarizations are taken to be longitudinal,
$\bar{\varepsilon} \rightarrow k$.
Furthermore, a simple calculation shows that the four-point correlation function of this theory satisfies the Jacobi identity of \cref{jacID} \emph{off-shell}. This ensures that color-kinematics duality holds to all multiplicity and loop order.
We also note that semi-YM does not have any ghosts from non-abelian gauge symmetry that could spoil color-kinematics at loop level. Due to the Feynman rules of this theory, the amplitudes are non-vanishing only at tree-level and one-loop. We demonstrate the implications of this property in \cref{2LoopObstruction}.

@@

Of course, dramatically altering the pole structure could spoil locality in the
double-copied theory.  As already mentioned, the only difference
classically between ZM and SDYM is the propagator structure.  While
both theories are color dual for the same reason, altering the
propagators has profound consequences since SDYM tree amplitudes
vanish and manifest color-kinematics does not persist to all loop
orders.

Color dual theories with the same interactions but different
kinetic terms have appeared in the literature before.  For example,
$J$-theory and the theory of non-Abelian fluids presented in
\cite{Cheung:2020djz} differ only in their propagators. Specifically,
taking the static limit of the fluid's $(D+1)$-dimensional kinetic
term $\partial_t - \nabla^2$ and Wick rotating one of the coordinates
yields the relativistic d'Alembertian of $D$-dimensional $J$-theory.

@@

\section{Spinor-helicity and conventions}\label{Conventions}

>>>>

Here we can think of the abelian vector as a background field that
sources on-shell $A_\mu$ currents. Indeed, as we describe in
\cref{sec:CKLagrangians}, semi-abelian Yang-Mills theory is at the
heart of $YZ$-theory \cite{Cheung:2016prv}, $J$-theory
\cite{Cheung:2020djz,Cheung:2021zvb}, and self-dual Yang-Mills
\cite{Monteiro2011pc}.  Specifically, semi-abelian YM is simply a
clever reinterpretation of the Lagrangian obtained by integrating an
auxiliary field into the $J$-theory equations of motion.  The Feynman
rule for the cubic vertex is
\begin{equation}\label{semiYMvert}
  \cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{}= (\varepsilon_1\bar{\varepsilon}_3)(\varepsilon_2 k_3)
  -  (\varepsilon_2\bar{\varepsilon}_3)(\varepsilon_1 k_3)
\end{equation}
where the incoming arrow is the abelianized gauge field, and the outgoing arrows the on-shell non-abelian vectors. The propagator is simply
\be\label{semiYMprop}
\propFrule{$A^\nu$}{$\bar{A}^\mu$}{$k \rightarrow $}{fermion2} = \frac{i}{k^2} \eta^{\mu\nu}.
\ee
We can use the Ward identity of
\cref{eq:GIrelA} to check that the amplitudes are indeed gauge
invariant when the \emph{abelian} polarizations are taken to be longitudinal,
$\bar{\varepsilon} \rightarrow k$.
Furthermore, a simple calculation shows that the four-point correlation function of this theory satisfies the Jacobi identity of \cref{jacID} \emph{off-shell}. This ensures that color-kinematics duality holds to all multiplicity and loop order.
We also note that semi-YM does not have any ghosts from non-abelian gauge symmetry that could spoil color-kinematics at loop level. Due to the Feynman rules of this theory, the amplitudes are non-vanishing only at tree-level and one-loop. We demonstrate the implications of this property in \cref{2LoopObstruction}.

@@

Of course, dramatically altering the pole structure could spoil locality in the
double-copied theory.  As already mentioned, the only difference
classically between ZM and SDYM is the propagator structure.  While
both theories are color dual for the same reason, altering the
propagators has profound consequences since SDYM tree amplitudes
vanish and manifest color-kinematics does not persist to all loop
orders.  Color dual theories with the same interactions but different
kinetic terms have appeared in the literature before.  For example,
$J$-theory and the theory of non-Abelian fluids presented in
\cite{Cheung:2020djz} differ only in their propagators. Specifically,
taking the static limit of the fluid's $(D+1)$-dimensional kinetic
term $\partial_t - \nabla^2$ and Wick rotating one of the coordinates
yields the relativistic d'Alembertian of $D$-dimensional $J$-theory.

@@

\subsection{Chern-Simons theory}
\label{sec:CSTheory}
The final theory that is unified by semi-abelian Yang-Mills is that Chern-Simons (CS) theory. As we will show below, plugging in appropriate on-shell states to the semi-YM ntegrands constructed in the text will produce precisely the kinematic numerators for this theory. Much like SDYM and ZM theory, the (CS) action as a preferred integer dimension of $D=3$,
\be
S_{\text{CS}} = \int d^3 x \,\text{tr}\left[\epsilon^{\mu\nu\rho} \left(A_\mu \partial_\nu A_\rho + \frac{2}{3}A_{\mu}A_{\nu}A_{\rho}\right)\right]
\ee
The color-dual properties of this theory was previously studied in ref.~\cite{Ben-Shahar:2021zww}, which demonstrated that color-kinematics duality is manifest off-shell. The Feynman rules for this theory can be pulled directly from the action, giving the following color-stripped three-point vertex and propagator:
\be\label{CSFrule}
\cubic{hgrey0}{nhpRed}{}{nhpRed}{}{nhpRed}{} = \epsilon^{\mu\nu\rho} \varepsilon^{\mu}_1\varepsilon^{\nu}_2\varepsilon^{\rho}_3 \qquad \qquad \propFrule{$A^\nu$}{$A^\mu$}{$k \rightarrow $}{nhpRed} = \frac{i}{k^2} \epsilon^{\mu\nu\rho} k^\rho
\ee
where $\epsilon^{\mu\nu\rho}$ is a 3D Levi-Civita symbol. At first glance, this seems far removed from the semi-abelian Yang-Mills analogs in \cref{semiYMvert} and \cref{semiYMprop}. However, the construct the on-shell amplitudes for CS theory, we must plug in the Fourier transforms of the on-shell currents, $\bar{\varepsilon}(p)$, as described in ref.~\cite{Ben-Shahar:2021zww}. These are related to the polarizations in the Feynman rules above as follows:
\be
\varepsilon^{\mu}(p) = \epsilon^{\mu\nu\rho} p^\nu \bar{\varepsilon}^\rho(p)
\ee
With this definition of the on-shell states, it is clear how the Feyman rules of \cref{CSFrule} is related to those of \cref{semiYMvert} and \cref{semiYMprop}: we simply must canonicalize the CS kinetic term by absorbing $ \epsilon^{\mu\nu\rho} k^\rho$ into the definition of the three-point vertex. 
\be
 \propFrule{$A^\nu$}{$A^\mu$}{$k \rightarrow $}{nhpRed} = \frac{i}{k^2} \epsilon^{\mu\nu\rho} k^\rho
\quad \longrightarrow \quad  \propFrule{$A^\nu$}{$\bar{A}^\mu$}{$k \rightarrow $}{fermion2} = \frac{i}{k^2} \eta^{\mu\nu}
\ee
This has the effect of orienting the three-point vertex of \cref{CSFrule}, by making the replacement $\varepsilon_i \rightarrow \epsilon^{\mu\nu\rho} k_i^\nu \bar{\varepsilon}^\rho_i$ on one of the legs:
\begin{align}
\cubic{hgrey0}{nhpRed}{}{nhpRed}{}{nhpRed}{} =  \epsilon^{\mu\nu\rho} \varepsilon^{\mu}_1\varepsilon^{\nu}_2 (\epsilon^{\rho \alpha \beta} k_3^\alpha \bar{\varepsilon}^\beta_3) =    (\varepsilon_1\bar{\varepsilon}_3)(\varepsilon_2 k_3)
  -  (\varepsilon_2\bar{\varepsilon}_3)(\varepsilon_1 k_3)
\end{align}
where we have used the identity, $\epsilon^{\mu\nu\rho}\epsilon^{\rho\alpha\beta} = \eta^{\mu \alpha} \eta^{\nu \beta} -  \eta^{\mu \beta} \eta^{\nu \alpha}$. Thus as desired, the CS vertex is precisely the three-point vertex of \cref{semiYMvert}. Moreover, in this form it is also clear how to map the $D$-dimensional amplitudes of semi-YM to the 3D observables of CS theory, one simply makes the following replacement on all the external states of semi-abelian YM, 
\be
\varepsilon^\mu_i \rightarrow \epsilon^{\mu\nu\rho} k^\nu_i \bar{\varepsilon}^\rho_i \qquad\qquad  \bar{\varepsilon}_i^\mu \rightarrow \bar{\varepsilon}^\mu_i
\ee
Upon making this replacement, one can map the amplitudes of $D$-dimensional semi-YM to 3D CS theory, $\mathcal{A}^{\text{semi-YM}}\rightarrow \mathcal{A}^{\text{CS}}$. While this may seem like a marginal gain at tree-level, by using our $D$-dimensional construction at one-loop, the manifestly color-dual integrands of \cref{SDYMnGon} can resolve regularization ambiguity of CS theory at loop-level due to its explicit dependence on $D=3$. For more background on CS theory, we refer the reader to ref.~\cite{Ben-Shahar:2021zww}.
\section{Spinor-helicity and conventions}\label{Conventions}
